Investigating Determinism of Physics Engines for usage in CAV and V\&V simulations

### 2021-04-20 document/source/body.tex
acks

>>>>

% ***************************************************
%  Thanks
% ***************************************************
\section*{Acknowledgement}
This research has in part been funded by the ROBOPILOT and CAPRI projects. Both projects are part-funded by the Centre for Connected and Autonomous Vehicles (CCAV), delivered in partnership with Innovate UK under grant numbers 103703 (CAPRI) and 103288 (ROBOPILOT), respectively. Special thanks to David May, CFMS, Auroch Digital and Fortelix for their discussions and support on this topic.
